
\begin{frame}[t]{Setting: balance laws}
\MyLogoa

\vspace{0.5cm}

We want to solve numerically  hyperbolic systems of balance laws

\begin{equation}
	\partial_tU+ \partial_x F(U)=  S(U)\partial_xH \nonumber
\end{equation}
 
\vspace{1.cm}

Typical examples  that we will use here


\begin{itemize}
\item Burger's equations 
\vspace{0.2cm}
\item Shallow water equations with topography
%\only<2->{\item{\bf Shallow water equations with topography/friction/Coriolis/etc}}
\end{itemize}

%\vspace{0.5cm}

% \flushright{\underline{We  consider both 1D and Multi-D problems}}
%\only<1>{\color{white}{\\[5pt] But for simplicity the discussion is done for the 1D case}}
%\only<3>{\\[5pt]But for simplicity the discussion is done for the 1D case}
\end{frame}
 

\begin{frame}[t]{Setting: balance laws}
\MyLogoa

\vspace{0.5cm}

We want to solve numerically  hyperbolic systems of balance laws

\begin{equation}
	\partial_tU+ \partial_x F(U)=  S(U)\partial_xH \nonumber
\end{equation}
 
 
 \vspace{0.5cm}

Shopping list


\begin{itemize}
\item Arbitrary high order
%\only<2->{\item{\bf Shallow water equations with topography/friction/Coriolis/etc}}
\item  Possibly monotonicity/positivity preserving  
%\only<2->{\item  Euler equations with gravity  $\leftarrow$ {\it and  some preliminary results here}  }
\item Steady state preserving 

\end{itemize}

\vspace{0.2cm}

  
 \end{frame}



\begin{frame}[t]{Objective}
\MyLogoa

\vspace{0.5cm}

We want to solve numerically  hyperbolic systems of balance laws

\begin{equation}
	\partial_tU+ \partial_x F(U)=  S(U)\partial_xH \nonumber
\end{equation}
 
 
 \vspace{0.5cm}
\begin{description}
	\item[The objective]  of well balanced schemes is to preserve exactly or with enhanced accuracy some of the steady state
	solutions.
	\vspace{0.1cm}
	\item[We focus] here on the development of well-balanced high order FD methods for general systems of balance laws that preserve all the stationary solutions.  
\end{description}


%Steady state preserving: on a given mesh we want to the scheme embed in the discretization a
%
%\begin{description} 
%
%\vspace{0.2cm}
%
%\item[{\it Definition}] of    $\partial_x F_{\textrm{h}} = S_{\textrm{h}}$ such that data  verifying it is exactly preserved
%
%\vspace{0.2cm}
%
%\item[{\it Projection}]    operator 
%providing such data, possibly different from the scheme
%
%\vspace{0.2cm}
%
%\item [{\it Characterization}]  of the above projection: e.g  enhanced consistency, well posedness 
%\end{description}
 
\end{frame}




\begin{frame}{Some approaches in the Bibliography  for 1D}
\MyLogoa

There are numberless approaches, and vast literature.
Related work:

\begin{enumerate}

\vspace{0.5cm}

\item Reconstruction/evolution of fluctuations wrt  discrete equilibria ({\bf approximate  full well balanced}):

\begin{itemize}
\item {\scriptsize    Castro \& Par\'es J.Sci.Comp. 2020,   G\'omez-Bueno et al, Appl.Math.Comp. 2021,   G\'omez-Bueno et al  athematics 2021,
Guerrero Fern\'andez et al  Mathematics 2021,   G\'omez-Bueno et al, Appl.Num.Math.  2023, etc. etc.}
\end{itemize}

\vspace{0.5cm}


\item Well balanced via integration of the source term and  global fluxes 

\begin{itemize}
\item {\scriptsize   Gasc\'on  \& Corber\'an  JCP 2001,  Donat \& Martinez-Gavara   J.Sci.Comp. 2011, 
Chertock et al JCP 2018, Cheng et al J.Sci.Comp. 2019, Mantri\&Noelle   JCP  2021,  
Ciallella et al.   J.Sci.Comp. 2023,   Xu and Shu J.Sci.Comp. to appear, etc. etc.} 
\end{itemize}

\vspace{0.5cm}


\item  Other approaches 

\begin{itemize}
\item Well balanced via reconstruction/evolution of fluctuations wrt to a given equilibrium
\item Preserving $V(u,\phi(x))=V_0$ via WB differencing or generalized polynomial approximations
\item Fully well balanced Riemann solver with 0-wave to enforce integral steady balance. 
\end{itemize}


\end{enumerate}


\end{frame}
 
 



